An Integral-field Spectroscopic Study of Low-power Radio Galaxies

### 2020-11-11 paper_noComments.tex
Final changes made?

% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype
% \usepackage{pdflscape} % for landscape pages
\usepackage{color,soul} % highlighting
\DeclareRobustCommand{\removed}[1]{{\sethlcolor{red}\hl{#1}}}
\DeclareRobustCommand{\added}[1]{{\sethlcolor{green}\hl{#1}}}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}

@@

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Key characteristics of our Southern Sample galaxies.}
    \label{tab:sample}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c l}
      \hline
      \hline
      Host galaxy & Radio source & Redshift & $S_\text{1.4\,GHz}$ & $m_K$ & Dust morphology\\
                  & (PKS) & & (mJy) & (mag) &\\
      \hline 
      ESO~443-G024 & 1258-321 & $0.01703$ & $1387\pm45$ & $8.51$ & no dust$^\text{a}$\\ 
      IC~1459 & 2254-367 & $0.00565$ & $1280\pm45$ & $6.81$ & dust lane$^\text{b}$\\
      IC~1531 & 0007-325 & $0.02553$ & $\leavevmode\phantom{0}388\pm12$ & $9.55$ & --\\
      IC~4296 & 1333-\leavevmode\phantom{0}33 & $0.01248$	& $1342\pm41$ & $7.50$ & edge-on disc$^\text{b}$\\
      NGC~612 & 0131-\leavevmode\phantom{0}36 & $0.02954$ & $\leavevmode\phantom{0}585\pm18$ & $9.58$ & dust lane$^\text{c}$\\
      NGC~1316 & 0320-\leavevmode\phantom{0}37 & $0.00591$ & $\leavevmode\phantom{0}255\pm10$ & $5.59$ & dust patches$^\text{b}$\\
      NGC~1399 & 0336-\leavevmode\phantom{0}35 & $0.00472$ & $\leavevmode\phantom{0}209\pm\leavevmode\phantom{0}7$ & $6.31$ & no dust$^\text{b}$\\
      NGC~3100 & 0958-314	& $0.00879$ & $\leavevmode\phantom{0}530\pm16$ & $8.08$ & dust lane$^\text{d}$\\
      NGC~3557 & 1107-372 & $0.01016$ & $\leavevmode\phantom{0}484\pm16$ & $7.20$ & face-on disc$^\text{b}$\\
      NGC~7075 & 2128-388 & $0.01819$ & $\leavevmode\phantom{0}837\pm28$ & $9.56$ & --\\
      -- & 0718-\leavevmode\phantom{0}34 & $0.02897$ & $1119\pm41$ & $9.97$ & dust patches$^\text{e}$\\
      \hline
      \hline
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: radio source name from the Parkes Southern
      Radio Source Catalogue (PKS). We hereafter refer to the last
      galaxy by its PKS name only. Col.~3: redshift \added{(uncertainty in redshift is $< 0.00001$)}. Col.~4: National
      Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
      $1.4$~GHz flux density \citep{Condon1998}. Col.~5: Two Micron
      All Sky Survey (2MASS) $K$-band apparent magnitude (with
      uncertainties of $\pm0.025$~mag;
      \citealt{Skrutskie2006}). Col.~6: dust morphology from (a)
      \citet{Govoni2000}, (b) \citet{Lauer2005}, (c)
      \citet{Bettoni2001}, (d) \citet{Sandage1979} and (e)
      \citet{Colbert2001}.}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

Next we implemented a routine to find the optimal initial values of
the redshift and velocity dispersion for each galaxy, to be used
subsequently when fitting individual bins. We used iterative fits to
the spatially-collapsed spectrum of each galaxy, i.e.\ the spectrum
resulting from summing across both spatial dimensions of the
datacube. We utilised the penalized pixel fitting (\textsc{pPXF})
routine\footnotemark[1] of \citet{Cappellari2004} and
\citet{Cappellari2016a} with the Medium-resolution Isaac Newton
Telescope (INT) Library of Empirical Spectra (MILES;
\citealt{Sanchez-Blazquez2006, Falcon-Barroso2011a}) to find the
best-fitting line-of-sight stellar velocity distribution (LOSVD) of
each collapsed spectrum, as parametrised by the Gaussian parameters
$V$, the mean velocity, and $\sigma$, the velocity dispersion. The
final mean stellar velocity of each galaxy is adopted as its precise
spectroscopic redshift and is listed in Table~\ref{tab:sample}. {\bf
  (Shouldn't there be an uncertainty on this redshift/mean velocity?
  List in Table~1.)} After this step, each bin is analysed
independently.

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
Clarify.)} stellar spectrum} \added{fits to the stellar 
spectrum for all bins}. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}

@@

In this analysis, we consider the following emission lines and
doublets: 
\added{[\ion{O}{II}]$\lambda\lambda$3726,3729,
H$\delta$,} H$\gamma$, H$\beta$,
[\ion{O}{iii}]$\lambda\lambda$4969,5007,
[\ion{N}{I}]$\lambda\lambda$5199,5202,
[\ion{O}{i}]$\lambda\lambda$6300,6363,
[\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
[\ion{S}{ii}]$\lambda\lambda$6716,6731 {\bf (Should the \ion{O}{ii}
  doublet discussed a few lines below also be quoted here? Or should
  the below be the \ion{O}{i} or \ion{O}{iii} doublet already quoted?
  What about H$\delta$, also in your original table but now commented
  out? Correct.)}. \removed{We fit the emission line fluxes and kinematics
independently of the stellar kinematics, and their fluxes
independently of each other (but see below).} To minimise template 
mismatch, whereby emission lines are erroneously fitted
to the edges of badly modelled and thus subtracted absorption features,
we follow the procedure set out in \citet{Sarzi2005}. In this method,
the stellar component is first fitted as above with potential emission
line regions masked, followed by the unmasking and fitting of the
[\ion{O}{iii}] doublet, again adopting a single
Gaussian template parametrised by $V$, the mean velocity, and
$\sigma$, the velocity dispersion. Setting this as the kinematics for 
all other emission lines, the amplitudes of the remaining
emission lines are fitted. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] 
and [\ion{N}{ii}] doublets, the two components of each doublet are fit 
with a fixed flux ratio of $3:1$, while the [\ion{N}{i}] doublet is 
fit with a fixed flux ratio of $3:2$ \citep{Safier1992}. The two 
components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit 
independently. {\bf (See previous comment about the \ion{O}{ii} doublet. 
Correct.)}.

@@

\removed{\subsubsection{Removing Emission Lines}}
% \label{subsubsec:RemovingEmission}

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
data, before the line strengths are measured. \removed{, using only the 
stellar templates (and continuum correction) subsequently considered 
for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
understand the second part of this sentence. Check/clarify/correct.)}}} 
These are then corrected for the effects of the stellar velocity 
dispersion, as detailed below.
% used for reconstructing the best-fit to

@@

In each bin, using the measured absorption line strengths, we identify
the best-fitting \added{luminosity-weighted} single stellar population (SSP) model from an
interpolated grid of models using \textsc{emcee}, a \textsc{python}
affine-invariant Markov-chain Monte-Carlo (MCMC) fitting package
\citep{Foreman-Mackey2013}. This grid is created by linearly
interpolating between the models of \citeauthor{Thomas2010}
(\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The
\citetalias{Thomas2010} models are chosen because they are based on
high-resolution flux-calibrated spectra, and therefore do not require
the absorption line strength measurements to be in the Lick/IDS
system.

@@

In reality, the field of view does not always \added{fully} contain 
\added{a given fitted ellipse} \removed{$1$~$R_\text{e}$}. When this 
is the case, we follow the method of \citet{Emsellem2007}, where 
$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
where $A_\text{s}$ is the area \added{contained within 
the field of view} of the {\bf (Largest? Clarify.)} 
\added{given} ellipse \removed{contained within 
the field of view}. {\bf (I do not understand the meaning of the 
following sentence in {\it italics}. Rephrase/explain better. 
Perhaps even simply remove? What are $R_\text{max}$ and 
$A_\text{ellipse}$?!)} {\it For a given galaxy, we fit ellipses 
as described above, up to $R_\text{m}=R_\text{max}$, where 
\added{$R_\text{max}$ is defined such that  
$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.} 
\removed{$A_\text{s}$ reaches a maximum difference of 15\% with 
respect to the area of the fitted ellipse, $A_\text{ellipse}$.}} The 
value $\epsilon_\text{e}$, the ellipticity \added{of this largest 
fitted ellipse} \removed{at $1$~$R_\text{e}$ or $R_\text{max}$, 
whichever is smallest}, is given in Column~3 of 
Table~\ref{tab:classify}.

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Kinematic classifications of our Southern Sample
      galaxies.}
    \label{tab:classify}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c c c c}
    \hline
    \hline
    Galaxy & $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR & Feature & Group 	\\
           & & & (deg)\\
      \hline 
      ESO~443-G024 & $0.048$ & $0.35$ & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
      IC~1459 & $0.125$ & $0.24$ & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
      IC~1531 & $0.101$ & $0.08$ & $-54\pm25$ & FR & NRR & LV & a \\
      IC~4296 & $0.034$ & $0.03$ & $\leavevmode\phantom{-0}8\pm12$ & SR & \leavevmode\phantom{N}RR & -- & e \\
      NGC~612 & $0.655$ & $0.36$ & $\leavevmode\phantom{-}12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
      NGC~1316 & $0.100$ & $0.39$ & $\leavevmode\phantom{-0}6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
      NGC~1399 & $0.090$ & $0.12$ & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
      NGC~3100 & $0.354$ & $0.24$ & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
      NGC~3557 & $0.312$ & $0.20$ & $\leavevmode\phantom{-}16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
      NGC~7075 & $0.068$ & $0.04$ & $\leavevmode\phantom{-}36\pm50$ & SR & NRR & -- & b \\
      PKS~718-34 & $0.159$ & $0.17$ & $\leavevmode\phantom{-}15\pm25$ & FR & NRR & KDC & b\\
      \hline
      \hline    
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: $\lambda_\text{R}$ evaluated at
      $R_\text{e}$. Col.~3: ellipticity evaluated at $R_\text{e}$ or
      $R_\text{max}$, whichever is smallest. Col.~4: misalignment
      angle between the photometric and stellar kinematic position
      angles. Col.~5: fast-/slow-rotator (FR/SR)
      classification. Col.~6: regular-/non-regular-rotator (RR/NRR)
      classification. Col.~7: kinematic features:
      kinematically-decoupled core (KDC) or low-velocity (LV). Col.~8:
      \citeauthor{Krajnovic2011}'s (\citeyear{Krajnovic2011})
      kinematic group. The kinematic group of PKS~718-34 is tentative;
      a higher $S/N$ is required in the outer parts of the field of
      view for confirmation. {\bf (It would be better to calculate and
        report/list uncertainties on $\lambda_\mathrm{R_e}$ and
        $\epsilon_\text{e}$.)}}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

The kinematic position angle, $PA_\text{kin}$, is defined as the angle
of the axis perpendicular to the apparent angular momentum vector,
measured \added{eastward} \removed{westward} from North. {\bf (Are you sure this is westward and
  not eastward? Position angles are usually defined from North to
  East, the latter of course usually being to the left in astronomical
  images. Check and correct if need be.)} A global value of
$PA_\text{kin}$ is calculated using the \textsc{python} routine
\textsc{fit\_kinematic\_pa}\footnotemark[1], that finds
$PA_\text{kin}$ of the symmetrised mean velocity map, as described in
Appendix~C of \citet{Krajnovic2006}.
% This routine finds a symmetric (about $PA_\text{kin}$) velocity
% field, by replacing the mean velocity, $V$, in each bin with
% \begin{equation}
% V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4}~,
% \end{equation}
% where $x$ and $y$ are the centroid coordinates of a given bin, with
% the origin at the centre of the galaxy and the x axis aligned along
% $PA_\text{kin}$. Linear interpolation is used where necessary.

Column~4 in Table~\ref{tab:classify} lists the misalignment angle
between the photometric and stellar kinematic position angles,
$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$
{\bf (Why is that different from simply
  $\Gamma_\text{kin}\equiv PA_\text{phot}-PA_\text{kin}$? Correct if
  need be.)} {\bf (At which radius/ellipse semi-major axis is
  $PA_\text{phot}$ taken/measured? Specify.)} \added{, where$PA_\text{phot}$ is measured at $R_\text{max}$.}

@@

We also make use of the Atlas$^\text{3D}$ specific angular momentum
parameter, $\lambda_\text{R}$ \citep{Emsellem2007}, evaluated at
$1$~$R_\text{e}$, where
\begin{equation}
  \lambda_\mathrm{R_e}\equiv\frac{\sum_{i=1}^{N}\,F_iR_i|V_i|}{\sum_{i=1}^{N}\,F_iR_i\sqrt{V_i^2+\sigma_i^2}}~,
\end{equation}
{\bf (Is $R_i$ really measured from the centre as stated, or rather
  with respect to the kinematic minor axis/rotation axis?
  State/explain if the latter. JW: Yes, $R_i$ is from the center - see Eq6 in \citep{Emsellem2007})} where $F_i$ is the flux of the
$i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
sum is computed over all $N$ bins within \removed{$1$~$R_\text{e}$} \added{$1$~$R_\text{max}$} of the
centre of the galaxy. {\bf (What do you do if the field of view does
  not reach $1$~$R_\text{e}$? Specify/discuss (as for
  $\epsilon_\text{e}$).)}

@@

We find $4$ out of $11$, or $36\pm15\%$, of our sample galaxies are
regular rotators. This compares to \added{$82\pm2\%$} of the Atlas$^\text{3D}$
galaxies being classified as regular rotators
\citep{Krajnovic2011}. {\bf (Better to also quote the uncertainty on
  that $82\%$ figure.)} However, the likelihood of a given galaxy
being a regular rotator is highly mass dependent, the likelihood
decreasing with increasing mass. As our Southern Sample galaxies are
all extremely massive, we naturally expect to find a higher fraction
of non-regular rotators than that of the Atlas$^\text{3D}$ sample.

>>>>

% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype
% \usepackage{pdflscape} % for landscape pages
\usepackage{color,soul} % highlighting

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Ilaria Ruffa,$^{4}$ Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ Rosita Paladino,$^{4}$ Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and Timothy Davis$^{5}$
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK

@@

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Key characteristics of our Southern Sample galaxies.}
    \label{tab:sample}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c l}
      \hline
      \hline
      Host galaxy & Radio source & Redshift & $S_\text{1.4\,GHz}$ & $m_K$ & Dust morphology\\
                  & (PKS) & & (mJy) & (mag) &\\
      \hline 
      ESO~443-G024 & 1258-321 & $0.01703$ & $1387\pm45$ & $8.51$ & no dust$^\text{a}$\\ 
      IC~1459 & 2254-367 & $0.00565$ & $1280\pm45$ & $6.81$ & dust lane$^\text{b}$\\
      IC~1531 & 0007-325 & $0.02553$ & $\leavevmode\phantom{0}388\pm12$ & $9.55$ & --\\
      IC~4296 & 1333-\leavevmode\phantom{0}33 & $0.01248$	& $1342\pm41$ & $7.50$ & edge-on disc$^\text{b}$\\
      NGC~612 & 0131-\leavevmode\phantom{0}36 & $0.02954$ & $\leavevmode\phantom{0}585\pm18$ & $9.58$ & dust lane$^\text{c}$\\
      NGC~1316 & 0320-\leavevmode\phantom{0}37 & $0.00591$ & $\leavevmode\phantom{0}255\pm10$ & $5.59$ & dust patches$^\text{b}$\\
      NGC~1399 & 0336-\leavevmode\phantom{0}35 & $0.00472$ & $\leavevmode\phantom{0}209\pm\leavevmode\phantom{0}7$ & $6.31$ & no dust$^\text{b}$\\
      NGC~3100 & 0958-314	& $0.00879$ & $\leavevmode\phantom{0}530\pm16$ & $8.08$ & dust lane$^\text{d}$\\
      NGC~3557 & 1107-372 & $0.01016$ & $\leavevmode\phantom{0}484\pm16$ & $7.20$ & face-on disc$^\text{b}$\\
      NGC~7075 & 2128-388 & $0.01819$ & $\leavevmode\phantom{0}837\pm28$ & $9.56$ & --\\
      -- & 0718-\leavevmode\phantom{0}34 & $0.02897$ & $1119\pm41$ & $9.97$ & dust patches$^\text{e}$\\
      \hline
      \hline
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: radio source name from the Parkes Southern
      Radio Source Catalogue (PKS). We hereafter refer to the last
      galaxy by its PKS name only. Col.~3: redshift (uncertainty in redshift is $< 0.00001$). Col.~4: National
      Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
      $1.4$~GHz flux density \citep{Condon1998}. Col.~5: Two Micron
      All Sky Survey (2MASS) $K$-band apparent magnitude (with
      uncertainties of $\pm0.025$~mag;
      \citealt{Skrutskie2006}). Col.~6: dust morphology from (a)
      \citet{Govoni2000}, (b) \citet{Lauer2005}, (c)
      \citet{Bettoni2001}, (d) \citet{Sandage1979} and (e)
      \citet{Colbert2001}.}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

Next we implemented a routine to find the optimal initial values of
the redshift and velocity dispersion for each galaxy, to be used
subsequently when fitting individual bins. We used iterative fits to
the spatially-collapsed spectrum of each galaxy, i.e.\ the spectrum
resulting from summing across both spatial dimensions of the
datacube. We utilised the penalized pixel fitting (\textsc{pPXF})
routine\footnotemark[1] of \citet{Cappellari2004} and
\citet{Cappellari2016a} with the Medium-resolution Isaac Newton
Telescope (INT) Library of Empirical Spectra (MILES;
\citealt{Sanchez-Blazquez2006, Falcon-Barroso2011a}) to find the
best-fitting line-of-sight stellar velocity distribution (LOSVD) of
each collapsed spectrum, as parametrised by the Gaussian parameters
$V$, the mean velocity, and $\sigma$, the velocity dispersion. The
final mean stellar velocity of each galaxy is adopted as its precise
spectroscopic redshift and is listed in Table~\ref{tab:sample}. 
After this step, each bin is analysed
independently.

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the fits to the stellar 
spectrum for all bins. For this reason, when fitting the stellar spectra
only (i.e.\ Sections~\ref{subsec:starKin}), the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA. The best-fitting stellar spectra were then extrapolated above 5800~\AA.

@@

In this analysis, we consider the following emission lines and
doublets: 
[\ion{O}{II}]$\lambda\lambda$3726,3729,
H$\delta$, H$\gamma$, H$\beta$,
[\ion{O}{iii}]$\lambda\lambda$4969,5007,
[\ion{N}{I}]$\lambda\lambda$5199,5202,
[\ion{O}{i}]$\lambda\lambda$6300,6363,
[\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
[\ion{S}{ii}]$\lambda\lambda$6716,6731. To minimise template 
mismatch, whereby emission lines are erroneously fitted
to the edges of badly modelled and thus subtracted absorption features,
we follow the procedure set out in \citet{Sarzi2005}. In this method,
the stellar component is first fitted as above with potential emission
line regions masked, followed by the unmasking and fitting of the
[\ion{O}{iii}] doublet, again adopting a single
Gaussian template parametrised by $V$, the mean velocity, and
$\sigma$, the velocity dispersion. Setting this as the kinematics for 
all other emission lines, the amplitudes of the remaining
emission lines are fitted. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] 
and [\ion{N}{ii}] doublets, the two components of each doublet are fit 
with a fixed flux ratio of $3:1$, while the [\ion{N}{i}] doublet is 
fit with a fixed flux ratio of $3:2$ \citep{Safier1992}. The two 
components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit 
independently.

@@

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
data, before the line strengths are measured. These are then corrected for the effects of the stellar velocity 
dispersion, as detailed below.
% used for reconstructing the best-fit to

@@

In each bin, using the measured absorption line strengths, we identify
the best-fitting luminosity-weighted single stellar population (SSP) model from an
interpolated grid of models using \textsc{emcee}, a \textsc{python}
affine-invariant Markov-chain Monte-Carlo (MCMC) fitting package
\citep{Foreman-Mackey2013}. This grid is created by linearly
interpolating between the models of \citeauthor{Thomas2010}
(\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The
\citetalias{Thomas2010} models are chosen because they are based on
high-resolution flux-calibrated spectra, and therefore do not require
the absorption line strength measurements to be in the Lick/IDS
system.

@@

In reality, the field of view does not always fully contain 
a given fitted ellipse. When this 
is the case, we follow the method of \citet{Emsellem2007}, where 
$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
where $A_\text{s}$ is the area contained within 
the field of view of the given ellipse. {\it For a given galaxy, we fit ellipses 
as described above, up to $R_\text{m}=R_\text{max}$, where 
$R_\text{max}$ is defined such that  
$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.
} The value $\epsilon_\text{e}$, the ellipticity of this largest 
fitted ellipse, is given in Column~3 of 
Table~\ref{tab:classify}.

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Kinematic classifications of our Southern Sample
      galaxies.}
    \label{tab:classify}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c c c c}
    \hline
    \hline
    Galaxy & $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR & Feature & Group 	\\
           & & & (deg)\\
      \hline 
      ESO~443-G024 & $0.048$ & $0.35$ & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
      IC~1459 & $0.125$ & $0.24$ & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
      IC~1531 & $0.101$ & $0.08$ & $-54\pm25$ & FR & NRR & LV & a \\
      IC~4296 & $0.034$ & $0.03$ & $\leavevmode\phantom{-0}8\pm12$ & SR & \leavevmode\phantom{N}RR & -- & e \\
      NGC~612 & $0.655$ & $0.36$ & $\leavevmode\phantom{-}12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
      NGC~1316 & $0.100$ & $0.39$ & $\leavevmode\phantom{-0}6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
      NGC~1399 & $0.090$ & $0.12$ & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
      NGC~3100 & $0.354$ & $0.24$ & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
      NGC~3557 & $0.312$ & $0.20$ & $\leavevmode\phantom{-}16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
      NGC~7075 & $0.068$ & $0.04$ & $\leavevmode\phantom{-}36\pm50$ & SR & NRR & -- & b \\
      PKS~718-34 & $0.159$ & $0.17$ & $\leavevmode\phantom{-}15\pm25$ & FR & NRR & KDC & b\\
      \hline
      \hline    
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: $\lambda_\text{R}$ evaluated at
      $R_\text{e}$. Col.~3: ellipticity evaluated at $R_\text{e}$ or
      $R_\text{max}$, whichever is smallest. Col.~4: misalignment
      angle between the photometric and stellar kinematic position
      angles. Col.~5: fast-/slow-rotator (FR/SR)
      classification. Col.~6: regular-/non-regular-rotator (RR/NRR)
      classification. Col.~7: kinematic features:
      kinematically-decoupled core (KDC) or low-velocity (LV). Col.~8:
      \citeauthor{Krajnovic2011}'s (\citeyear{Krajnovic2011})
      kinematic group. The kinematic group of PKS~718-34 is tentative;
      a higher $S/N$ is required in the outer parts of the field of
      view for confirmation.}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

The kinematic position angle, $PA_\text{kin}$, is defined as the angle
of the axis perpendicular to the apparent angular momentum vector,
measured eastward from North. A global value of
$PA_\text{kin}$ is calculated using the \textsc{python} routine
\textsc{fit\_kinematic\_pa}\footnotemark[1], that finds
$PA_\text{kin}$ of the symmetrised mean velocity map, as described in
Appendix~C of \citet{Krajnovic2006}.
% This routine finds a symmetric (about $PA_\text{kin}$) velocity
% field, by replacing the mean velocity, $V$, in each bin with
% \begin{equation}
% V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4}~,
% \end{equation}
% where $x$ and $y$ are the centroid coordinates of a given bin, with
% the origin at the centre of the galaxy and the x axis aligned along
% $PA_\text{kin}$. Linear interpolation is used where necessary.

Column~4 in Table~\ref{tab:classify} lists the misalignment angle
between the photometric and stellar kinematic position angles,
$\Gamma_\text{kin}\equiv\arcsin(\sin[PA_\text{phot}-PA_\text{kin}])$, 
where$PA_\text{phot}$ is measured at $R_\text{max}$.

@@

We also make use of the Atlas$^\text{3D}$ specific angular momentum
parameter, $\lambda_\text{R}$ \citep{Emsellem2007}, evaluated at
$1$~$R_\text{e}$, where
\begin{equation}
  \lambda_\mathrm{R_e}\equiv\frac{\sum_{i=1}^{N}\,F_iR_i|V_i|}{\sum_{i=1}^{N}\,F_iR_i\sqrt{V_i^2+\sigma_i^2}}~,
\end{equation}
where $F_i$ is the flux of the
$i^\text{th}$ bin, $R_i$ its distance from the centre, $V_i$ its mean
stellar velocity and $\sigma_i$ its stellar velocity dispersion. The
sum is computed over all $N$ bins within $1$~$R_\text{max}$ of the
centre of the galaxy.

@@

We find $4$ out of $11$, or $36\pm15\%$, of our sample galaxies are
regular rotators. This compares to $82\pm2\%$ of the Atlas$^\text{3D}$
galaxies being classified as regular rotators
\citep{Krajnovic2011}. However, the likelihood of a given galaxy
being a regular rotator is highly mass dependent, the likelihood
decreasing with increasing mass. As our Southern Sample galaxies are
all extremely massive, we naturally expect to find a higher fraction
of non-regular rotators than that of the Atlas$^\text{3D}$ sample.
